\textbf{Title}

### 2015-06-05 paper/draft_3.tex
small changes to paper and draft

We first consider the application of ASH in the context of the nonparametric regression model with i.i.d. Gaussian errors that are spatially structured. Specifically, consider the model

@@

for $i=1,...,n$, where $\bm{Y}$ is the vector of observations, $\bm{\mu}$ is the mean curve sampled on an equally spaced grid, and $\Ge_i$ are independent $N(0,\s^2)$ noise. Assume that $n=2^J$ for some integer $J$, as is standard in the wavelet literature. To better understand and motivate our method, we first look at wavelet shrinkage from a Bayesian perspective.\bigskip\\
Given an orthogonal $n\times n$ matrix $W$ representing the orthonormal wavelet basis chosen, we have that the wavelet coefficients $\bm{d}$ are given by

@@

where $\mathbb{V}(Y)=\s^2I$. Hence, we can easily see that

>>>>

Consider the nonparametric regression model with i.i.d. Gaussian errors:

@@

for $i=1,...,n$, where $\bm{Y}$ is the vector of observations, $\bm{\mu}$ is the mean curve, and $\Ge_i$ are independent $N(0,\s^2)$ noise. Assume that $n=2^J$ for some integer $J$, as is standard in the wavelet literature. To motivate our method, we first describe wavelet shrinkage from a Bayesian perspective.

The wavelet coefficients $\bm{d}$ are given by

@@

\end{eqnarray
where $W$ denotes the orthogonal $n\times n$ matrix corresponding to the orthonormal wavelet basis chosen.
Since $\mathbb{V}(Y)=\s^2I$,
